\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-09 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

\author{Abhishek~Halder,~\IEEEmembership{Senior Member,~IEEE,} 
%\author{Abhishek~Halder,~\IEEEmembership{Member,~IEEE,}
Xinbo~Geng,~\IEEEmembership{Member,~IEEE,}
        Kenneth~F. Caluya,
        and~Pegah~Ojaghi% <-this % stops a space
\thanks{A. Halder and K.F. Caluya are with the Department of Applied Mathematics, University of California, Santa Cruz, CA 95064, USA, {\texttt{\{ahalder,kcaluya\}@ucsc.edu}}.}% <-this % stops a space
\thanks{X. Geng is with the School of Electrical and Computer Engineering, Cornell University, Ithaca, NY 14850, USA, {\texttt{xg72@cornell.edu}}.} %
\thanks{P. Ojaghi is with the Department of Computer Science and Engineering, University of California, Santa Cruz, CA 95064, USA, {\texttt{pojaghi@ucsc.edu}}.}%
\thanks{This research was partially supported by the NSF award 1923278.}}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\linewidth]{IEEE14marginals.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs of the generator $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup described in Sec. \ref{subsec:NumSimIEEEBus}. The $5$ rows above correspond to the $5$ generator nodes; these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginals}
\end{figure*}

>>>>

\author{Abhishek~Halder,~\IEEEmembership{Senior Member,~IEEE,} 
%\author{Abhishek~Halder,~\IEEEmembership{Member,~IEEE,}
        Kenneth~F. Caluya,
        Pegah~Ojaghi,
        and~Xinbo~Geng,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{A. Halder and K.F. Caluya are with the Department of Applied Mathematics, University of California, Santa Cruz, CA 95064, USA, {\texttt{\{ahalder,kcaluya\}@ucsc.edu}}.}% <-this % stops a space
\thanks{X. Geng is with the School of Electrical and Computer Engineering, Cornell University, Ithaca, NY 14850, USA, {\texttt{xg72@cornell.edu}}.} %
\thanks{P. Ojaghi is with the Department of Computer Science and Engineering, University of California, Santa Cruz, CA 95064, USA, {\texttt{pojaghi@ucsc.edu}}.}%
\thanks{This research was partially supported by the NSF award 1923278.}}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\linewidth]{IEEE14marginals.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs of the generator $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup described in Sec. \ref{subsec:NumSimIEEEBus}. The $5$ rows above correspond to the $5$ generator nodes; these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values. The $\theta_i$ are in rad, the $\omega_i$ are in rad/s.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginals}
\end{figure*}
